Draft

### 2017-05-31 Thesis/Draft.Rmd
Add start of chapter three

---
title: "On the Complexity of Best Arm Identification"
author: "Tim Radtke"
date: "5/20/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

>>>>

---
title: "Draft"
author: "Tim Radtke"
date: "5/28/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 3
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

# Thresholding Bandit Problem

The *Thresholding Bandit Problem* described in Locatelli et al. (2016) can be considered a variant of a variant. It can be framed into the wider literature of *Pure Exploration* multi-armed bandit problems. In particular, it shares characteristics with the *Top-$m$* problem. This problem is concerned with finding the $m$ best arms as described by the means of their corresponding distributions. This in turn is similar to the *combinatorial bandit* problem, which also aims at finding the $m$ best arms. However, it is able to pull several arms at once: Think of an online shop that shows five recommended products on a product detail page. These five recommended products might each be represented by an arm, and we look for the products with the largest mean conversion rate. The thresholding bandit problem we discuss here, however, is concerned with pulling a single arm at a time. And so a more appropriate situation is that of a website presenting a banner. Again, think of an online shop trying to promote a certain category. The content team came up with a number of different designs for the banner, and it's not clear how many click-throughs they will gather.

The idea now is that we would like to classify the banners into two distinct groups: A group with a mean conversion rate $\mu_i$ below threshold $\tau$, and a group with mean conversion rate $\mu_i$ above threshold $\tau$. This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.

If it turns out that in general we can find relatively quickly whether arms are above or below a threshold, then this kind of test can be used to safeguard against very bad versions in a test. Before we move to a Top-$m$ test, we might want to run a thresholding version and then continue only with the arms classified into the group above the threshold. This might be justified when adjusting parts of the checkout process of an online shop, where the conversion rate or the average order value should not drop below a threshold.

## Setup

In any case, the problem boils down to the following. As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$. We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed accoring to the arm's distribution $\nu_k$. In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$. In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means. In the case of pure exploration bandits, it is for example necessary to compare the arms because one aims to find the best one. In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment. One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront. We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow a $R$-sub-Gaussian distribution. Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound. Both hinge upon the *complexity* of a given problem. Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others. Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold. Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it will be to distinguish the two successfully based on samples from the distribution $\nu_i$. For the case of the sub-Gaussian distributions, a natural measure of this distance is given by simply $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.

If we extend this idea to the set of arms $i \in \{1,...,K\}$ of a given bandit problem, a natural measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$. In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify. (WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM? WHAT IS ITs MOTIVATION? ITS NOT THAAAT NATURAL)

We also see that this definition may lose relevancy as we move away from $R$-sub-Gaussian distributions. (ADD QUICK EXAMPLE OF WHAT CHANGES; REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)

Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize. As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret. The notion of regret considered in the thresholding bandit, however, is more akin to the regret in pure exploration bandits or the error probability in sequential hypothesis testing. Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm. Or, more rigorously, let us define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$. Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$. At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$. We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$. Let $T$ be the overall number of samples the algorithm is allowed to pull. We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$. That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified. It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss. These arms are considered close enough to the threshold that we do not care whether they lie above or below.

ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS

From there, it is natural to define the expected regret/loss as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$. This, of course, is the mentioned probability of making a mistake.

ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS

Lastly, it is to mention that we are considering the fixed-budget version of the thresholding bandit problem. We thus fix the number of samples that the algorithm will pull upfront at $T$. The task of the algorithm is then to find a sampling rule or strategy which distributes the budget $T$ among the $K$ arms in such a way that the expected regret, or the error probability, is minimized. In other terms, the algorithm aims to use the $T$ samples in a way that lets him return the two sets $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}_{\tau}^C$ with as much confidence as possible. This again shows the contrast to the fixed confidence setting in which one fixes the confidence level upfront and lets the algorithm draw as many samples as necessary to reach the required confidence.

At this point, we have defined the fixed budget thresholding bandit setup for any algorithm in the case of sub-Gaussian distributions. We thus proceed to describe the algorithm proposed in Locatelli et al. (2016).

## The APT Algorithm

In the following we describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al. (2016), which is a simple yet effective algorithm and displays some very favorable characteristics when compared with alternative algorithms.

From the general setup, we already know how the algorithm will end. After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated until time $T$. Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$. For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including). Consequently, the empirical mean of arm $i$ at time $t$ is given by $\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.

To be specific, the APT algorithm initiates by pulling each arm once. Then, for each $t > K$, it calculates for every arm the values $T_i(t)$ and $\mu_i(t)$. Based on the empirical mean, the algorithm computes the estimated gap between the mean and the threshold as $\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon$. The decision of which arm is sampled next is then based on the value $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)$: the algorithm pulls arm $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$ minimizing this decision quantity. After $T$ pulls overall, the arm returns the sets described in the general setup, $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}^C_{\tau}$.

**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$. This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most. That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold. In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$. Consequently, other arms farther away from the threshold will be sampled again. In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision. Of course, that's just Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate.

## Discussion

One of the APT algorithm's main features is its simplicity. The sampling rule is very straightforward, and, as highlighted in Locatelli et al. (2016), it does not require any knowledge about the type of sub-Gaussianity $R$, or the complexity $H$ upfront. This makes the algorithm immediately applicable in practice while it still enjoys its upper bound on the expected regret. This is in particular worth highlighting when comparing APT to algorithms used in the pure exploration bandit setting. There, many algorithms require knowledge about the corresponding complexity upfront. The problem however being, that to know the complexity, the experimenter has to know all means up to a permutation of the arms (for example, see Audibert et al., 2010). This, of course, is not given in practice and thus alternative algorithms try to estimate the complexity online which is not a desirable solution either as especially in the beginning plug-in estimates based on the estimated means may lead to wrong estimates of the complexity and consequently budget allocation based on mistaken beliefs (compare Garivier and Kaufmann, 2016).

Furthermore, Locatelli et al. (2016) were able to present an upper bound for the APT algorithm matching the lower bound in their Theorem 1. Proofs of both bounds are given below.

Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian. This is mentioned in Locatelli et al. (2016). In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta_i}(t)$ are motivated by (sub-)Gaussian distributions. The more one moves away from Gaussian-like distributions, the less appropriate this term becomes, however. In particular, the empirical mean will be less concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions. Locatelli et al. (2016) thus refers to Bubeck et al. (2013) which considers solutions for multi-armed bandits that are based on heavy-tail distributions. By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.

Another step towards dealing with non sub-Gaussianity is made by Mukherjee et al. (2017) who use an estimate of the variance additionally to the empirical mean in their Augmented UCB solution. Utilizing this additional information, the algorithm seems to perform better than for example APT, going from simulation results displayed in the paper. We will continue to discuss the Augmented UCB solution further in chapter 3.

Yet another idea, again mentioned in Locatelli et al. (2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly. While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian. This, for example, is the case for Bernoulli distributions at very small parameters $\mu$. It's quite obvious simply by looking at examples that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation. The second graph then shows, that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values. Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.

Refer also to page 6 in Kaufmann et al. (2016): "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ defined in (2) as a subgaussian approximation".

And so a potential approach can be to use the Kullback-Leibler divergence as measure similar to the methods proposed in Kaufmann et al. (2015). They proposed Kullback-Leibler based approaches for the pure exploration bandit setting, which we will describe in chapter 2. Then, in chapter 3, we will come back to the problem of using the Kullback-Leibler divergence in the thresholding bandit setting.

```{r, echo = FALSE}
KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
par(mfcol = c(1,2))

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
     xlab = "p_1", ylab = "KL(Ber(p_1),Ber(p_2))", main = "KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
       KL_ber(seq(0.00001,0.3, by = 0.000005),i))
}

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
     xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        (seq(0.00001,0.3, by = 0.000005)-i)^2)
}
par(mfcol = c(1,1))
```

```{r, echo = FALSE}
KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
par(mfcol = c(1,2))

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
     xlab = "p_1", ylab = "KL(Ber(p_2),Ber(p_1))", main = "KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        KL_ber(i,seq(0.00001,0.3, by = 0.000005)))
}

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
     xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        (i-seq(0.00001,0.3, by = 0.000005))^2)
}
par(mfcol = c(1,1))
```

## Lower Bound: Theorem and Proof

\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
\label{theorem:Locatelli2016Theorem1}
For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1. Lower bound the largest probability of error among these problems for the best possible algorithm as follows. Let $K,T \geq 0$. Let for any $i \leq K$, $d_i \geq 0$. Let $\tau \in \mathbb{R}, \epsilon > 0$.

For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise. For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.

It holds that for any bandit algorithm,

\begin{equation*}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
\end{equation*}

where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
\end{theorem}

*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem 1 of Locatelli et al. (2016), a lower bound for the thresholding bandit problem is shown. The basic idea is as follows. The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions. To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario. Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).

To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g. If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$. Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$. Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$. It is easy to see that in this case, this is equivalent to a "flip around the threshold". Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.

The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms. Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$. This is a product distribution where the $K$ different means all lie above the threshold. We would hope that an algorithm classifies the means accordingly. However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$). We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.

For each of the $K$ arms, we introduce an alternative model of the following kind. Before the start of the algorithm, we introduce a slight variation in the setup. The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem. However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$. Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above. Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$. This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.

As in Locatelli et al. (2016), we let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ define the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e. according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$. $(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.

#### Reminder about the goal of the proof

At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(d_k)_k$. We will now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.

#### Statistical Decision

Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means. In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$. Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$. Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.

In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$. Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$. The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$. However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models. We can write this now as

\begin{align}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
\end{align}

In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$. This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state. In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor. This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$. By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.

We will define the change of distribution in terms of the empirical log-likelihood for our case. Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence. So let us first introduce the empirical Kullback-Leibler divergence.

Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$. Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively. For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence as

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
\end{align*}

Since we consider Gaussian distributions with variance 1, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$. Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
\end{align*}

#### Change of Distribution

We are now ready to state the change of distribution. As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$. When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took. The change of distribution is then defined as:

\begin{align*}
\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
\end{align*}

Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$. Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.

#### Concentration of the Empirical Kullback-Leibler Divergence

For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.

It is easy to see that

\begin{equation*}
|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
\end{equation*}

itself is a normally distributed random variable with mean zero and a variance decreasing in $t$. Thus, one can show as in Locatelli et al. (2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event

\begin{equation}
\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
\end{equation}

Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:

\begin{align*}
\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound. Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.

#### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$

Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that. In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$. Thus we can write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.

What is left to show before we have our final bound is a bound on $T_i$. To show that any algorithm has a certain bound on its error, it only makes sense that every arm has to pulled at least a certain amount of times. Consequently, no arm should be pulled exclusively.

First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
\end{align*}

Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$. The latter holds since any reasonable algorithm has to check each arm at least once in our setup. This is because we need to check each arm's performance in comparison to the threshold. Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$. To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$. This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.

So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
\end{align*}
